### 2017-09-25 Documents/bootcamp_topic_pyfun2.tex
Pyfun2 outline updates

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
\centerline{Revised: \today}

@@

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice, stickers
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}

@@

\section*{After class}

>>>>

%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../LaTeX/undergrad_preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Python Fundementals 1}
\runningheader{}{}{}
\runningfooter{}{}{}

\begin{document}
\parskip=\bigskipamount

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
\medskip
\centerline{Revised: \today}

@@

\begin{itemize}
\item  Today's handouts:  this outline, stickers
\item  All posted on {\it Topic outlines \& book \& links\/} page of website (except the stickers).
\end{itemize}

@@

\section*{After this module}
